---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/word2vec.r.svg?branch=master)](https://travis-ci.org/news-r/word2vec.r)
<!-- badges: end -->

# word2vec.r

`word2vec.r` is an R wrapper to the `Word2Vec.jl` Julia package.

## Installation

Being a wrapper to a [Julia](https://julialang.org/) package, `word2vec.r` requires the latter to be installed.

You can install the package from Github with:

``` r
# install.packages("remotes")
remotes::install_github("news-r/word2vec.r")
```

## Examples

You _must_ run `setup_word2vec` at the begining of every session, you will otherwise encounter errors and be prompted to do so.

```{r}
library(word2vec.r)

# setup word2vec Julia dependency
setup_word2vec()
```

The package comes with a dataset, [Macbeth by Shakespeare](https://en.wikipedia.org/wiki/Macbeth). However, being a corpus of 17,319 words it is not lazyly loaded and needs to be imported manually with the `data` function.

```{r}
data("macbeth", package = "word2vec.r")
```

### Word Vectors

With data we can train a model and extract the vectors.

```{r}
model_path <- word2vec(macbeth) # train model
model <- word_vectors(model_path) # get word vectors
```

There are then a multitude of functions one can use on the model.

- `get_vector`
- `vocabulary`
- `in_vocabulary`
- `size`
- `index`
- `cosine`
- `cosine_similar_words`
- `similarity`
- `analogy`
- `analogy_words`

All are well documented and have examples, visit their respective man pages with i.e.: `?get_vector`. Note that since all the functions listed above require the output of `word_vectors` (the `model` object in our case). Therefore a convenient reference class also exists.

__Functional__

```{r}
# words similar to king
cosine_similar_words(model, "king", 5L)

# size of model
size(model)
```

__Reference Class__

```{r}
wv <- WordVectors$new(model)
wv$get_vector("macbeth")
wv$cosine("rosse")
```

### Word Clusters

You 

```{r}
model_path <- word2clusters(macbeth, classes = 50L) # train model
model <- word_clusters(model_path)
```

__Functional__

```{r}
get_cluster(model, "king")
get_cluster(model, "macbeth")
```

__Reference Class__

```{r}
wc <- WordClusters$new(model)
wc$get_words(4L)
wc$vocabulary("rosse")
```