---
title: "word2vec"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{word2vec}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You _must_ run `setup_word2vec` at the begining of every session, you will otherwise encounter errors and be prompted to do so.

```{r}
library(word2vec.r)

# setup word2vec Julia dependency
setup_word2vec()
```

The package comes with a dataset, [Macbeth by Shakespeare](https://en.wikipedia.org/wiki/Macbeth). However, being a corpus of 17,319 words it is not lazyly loaded and needs to be imported manually with the `data` function. Note that the dataset is mildly preprocessed, all words are lowercase and punctuation has been removed.

```{r}
data("macbeth", package = "word2vec.r")
```

## Functions

With data we can train a model and extract the vectors.

```{r}
model_path <- word2vec(macbeth) # train model
model <- word_vectors(model_path) # get word vectors
```

There are then a multitude of functions one can use on the model.

- `get_vector`
- `vocabulary`
- `in_vocabulary`
- `size`
- `index`
- `cosine`
- `cosine_similar_words`
- `similarity`
- `analogy`
- `analogy_words`

All are well documented and have examples, visit their respective man pages with i.e.: `?get_vector`. Note that since all the functions listed above require the output of `word_vectors` (the `model` object in our case). Therefore a convenient reference class also exists.

## Functional

```{r}
# words similar to king
cosine_similar_words(model, "king", 5L)

# size of model
size(model)
```

## Reference Class

Because everything depends on the vectors (`model` object in our case) we provide reference class which limits the repetitive specification of said model as first argument to all functions.

```{r}
wv <- WordVectors$new(model)
wv$get_vector("macbeth")
wv$cosine("rosse")
```
